---
title: "R Notebook"
output: html_notebook
---

Add a new chunk by clicking the \*Insert Chunk\* button on the toolbar or by pressing \*Ctrl+Alt+I\*.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
#check working directory
setwd("C:/Users/hanji/Desktop/Workshop/Foldable_Spaces/Data")
getwd()
```

```{r}
#demographics
dm_raw <- read.csv("results_survey.csv") #, header = TRUE, sep = ",")

#user experience
dm_exp <- c(rep(1,sum(demographics$D3=="AO01")),rep(2,sum(demographics$D3=="AO02")),rep(3,sum(demographics$D3=="AO03")),rep(4,sum(demographics$D3=="AO04")),rep(5,sum(demographics$D3=="AO05")),rep(6,sum(demographics$D3=="AO06")),rep(7,sum(demographics$D3=="AO07")))
           
#male,female,etc.
demographics <- dm_raw[c(7,9:15)]

paste("total participants:",nrow(demographics))
paste("Female: ", sum(demographics$D1=="AO01"))
paste("Male: ", sum(demographics$D1=="AO02"))

paste("mean age: ",mean(demographics$D2))
paste("sd age: ",sd(demographics$D2))
paste("min age: ",min(demographics$D2))
paste("max age: ",max(demographics$D2))

paste("mean experience: ",mean(dm_exp))
paste("sd experience: ",sd(dm_exp))
```

```{r}
#Load raw file from limesurvey
raw = read.csv("results_survey.csv")


```

```{r}
#import .csv into Global Environment
acc1 <- read.csv("001_1AccordionTest_2021-10-22_143121.csv", header = FALSE, sep = ",") 

#make scatterplot
plot(acc1$V3,acc1$V4, main = paste(acc1$V1[1],"_Accordion"), xlab = "X", ylab = "y")



```
