---
title: "Main"
output: html_notebook
---

Add a new chunk by clicking the \*Insert Chunk\* button on the toolbar or by pressing \*Ctrl+Alt+I\*.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

```{r}
#check working directory
setwd("C:/Users/hanji/Desktop/Workshop/Foldable_Spaces/Data")
setwd("C:/Users/Jihae Han/Desktop/Projects/Foldable_Spaces/Data")
getwd()
library(ggplot2)
library(dplyr)
library(gtools)
library(ggpubr)
library(likert)
```

```{r}
#demographics
dm_raw <- read.csv("results_survey.csv") #, header = TRUE, sep = ",")

#male,female,etc.
demographics <- dm_raw[c(7,9:15)]
dm_ID <- seq(1,nrow(demographics))

#user experience
dm_exp <- c(rep(1,sum(demographics$D3=="AO01")),rep(2,sum(demographics$D3=="AO02")),rep(3,sum(demographics$D3=="AO03")),rep(4,sum(demographics$D3=="AO04")),rep(5,sum(demographics$D3=="AO05")),rep(6,sum(demographics$D3=="AO06")),rep(7,sum(demographics$D3=="AO07")))

paste("total participants:",nrow(demographics))
paste("Female: ", sum(demographics$D1=="AO01"))
paste("Male: ", sum(demographics$D1=="AO02"))

paste("mean age: ",mean(demographics$D2))
paste("sd age: ",sd(demographics$D2))
paste("min age: ",min(demographics$D2))
paste("max age: ",max(demographics$D2))

paste("mean experience: ",mean(dm_exp))
paste("sd experience: ",sd(dm_exp))
```

```{r}
#auxilary functions
substrRight <- function(s){
  substr(s, nchar(s), nchar(s))
}
intRight <- function(s){
  as.integer(substr(s, nchar(s), nchar(s)))
}
code2trial <-function(code){
  switch(intRight(code),"S&R", "Hor", "Ver", "Acc","Pre")
}
```

```{r}
#main functions 
checkNormalDistribution5 <- function(data,parameter) {
  sw1 <- shapiro.test(data[data$Condition=='Acc',][[parameter]])
  sw2 <- shapiro.test(data[data$Condition=='Ver',][[parameter]])
  sw3 <- shapiro.test(data[data$Condition=='Hor',][[parameter]])
  sw4 <- shapiro.test(data[data$Condition=='S&R',][[parameter]])
  sw5 <- shapiro.test(data[data$Condition=='Pre',][[parameter]])
  
  print(paste("Shapiro N.Distr. (including 'Pre'): ",sw1$p.value>=.05 & sw2$p.value>=.05 & sw3$p.value>=.05 & sw4$p.value>=.05 & sw5$p.value>=.05," ",parameter))

}
checkNormalDistribution <- function(data,parameter){
  sw1 <- shapiro.test(data[data$Condition=='Acc',][[parameter]])
  sw2 <- shapiro.test(data[data$Condition=='Ver',][[parameter]])
  sw3 <- shapiro.test(data[data$Condition=='Hor',][[parameter]])
  sw4 <- shapiro.test(data[data$Condition=='S&R',][[parameter]])
  
  print(paste("Shapiro N.Distr.: ",sw1$p.value>=.05 & sw2$p.value>=.05 & sw3$p.value>=.05 & sw4$p.value>=.05," ",parameter))
}
plotTheme <- theme(
  plot.title = element_text(hjust = 0.5),
  plot.subtitle = element_text(hjust = 0.5)
)
createBoxplot <- function(dataIn, parameter, title, pw, ylab=""){
  data <- dataIn # can optionally change this to make a copy instead of reference
  data$value <- data[[parameter]]
  ma <- max(data$value)
  mi <- min(data$value)
  step <- (ma - mi) / 10
  means <- aggregate(value ~  Condition, data, mean)
  means$value <- round(means$value, digits = 2)
  
  sds <- round(aggregate(value ~ Condition, data, sd)$value, digits=2)
  
  g <- ggplot(data, aes(x=Condition, y=value)) + 
    geom_boxplot(aes(fill=Condition), outlier.size = .6) +
    labs(title = title) +
    ylab(ylab) +
    stat_summary(fun=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE) + 
    geom_text(data = means, aes(label = paste("M=",means$value), y = means$value - 0.45 * step), family = "LM Roman 10") +
    plotTheme
  if (!missing(pw)){
    temp <- pw$p.value
    df <- data.frame(expand.grid(dimnames(temp)),array(temp))
    df <- na.omit(df)
    df$p <- df$array.temp.
    df$group1 <- df$Var1
    df$group2 <- df$Var2
    df$stars <- stars.pval(df$p)
    df$y.position <- c(ma + 1 * step, ma + 3*step,ma + 5*step,ma + 2*step,ma + 4*step,ma + 1*step)
    
    g <- g  + stat_pvalue_manual(df, label = 'stars', hide.ns=TRUE)
  }
  g
}
createBoxplot5 <- function(dataIn, parameter, title, pw, ylab=""){
  data <- dataIn # can optionally change this to make a copy instead of reference
  data$value <- data[[parameter]]
  ma <- 100
  mi <- -100
  step <- 20
  means <- aggregate(value ~  Condition, data, mean)
  means$value <- round(means$value, digits = 2)
  
  sds <- round(aggregate(value ~ Condition, data, sd)$value, digits=2)
  
  g <- ggplot(data, aes(x=Condition, y=value)) + 
    ylim(-100,100) +
    geom_boxplot(aes(fill=Condition), outlier.size = .6) +
    labs(title = title) +
    ylab(ylab) +
    stat_summary(fun=mean, colour="darkred", geom="point", shape=18, size=3,show.legend = FALSE) + 
    geom_text(data = means, aes(label = paste("M=",means$value), y = means$value - 0.45 * step), family = "LM Roman 10") +
    plotTheme
  if (!missing(pw)){
    temp <- pw$p.value
    df <- data.frame(expand.grid(dimnames(temp)),array(temp))
    df <- na.omit(df)
    df$p <- df$array.temp.
    df$group1 <- df$Var1
    df$group2 <- df$Var2
    df$stars <- stars.pval(df$p)
    df$y.position <- c(ma + 1 * step, ma + 3*step,ma + 5*step,ma + 2*step,ma + 4*step,ma + 1*step)
    
    g <- g  + stat_pvalue_manual(df, label = 'stars', hide.ns=TRUE)
  }
  g
}
```

```{r}
##---------- PRESENCE ----------##

#Load raw file from limesurvey
raw = read.csv("results_survey.csv")
offset = 69-33

#setup SUS presence
SUSpresence = data.frame(ID=NA, Condition=NA, SUSq1=NA, SUSq2=NA, SUSq3=NA, SUSq4=NA, SUSq5=NA, SUSq6=NA)
SUSpresence <- SUSpresence[FALSE,]

sus1 <- raw[c(1,33,47:52)]
sus2 <- raw[c(1,33+offset,47:52+offset)]
sus3 <- raw[c(1,33+offset*2,47:52+offset*2)]
sus4 <- raw[c(1,33+offset*3,47:52+offset*3)]

sus1[1] <- dm_ID
sus2[1] <- dm_ID
sus3[1] <- dm_ID
sus4[1] <- dm_ID

names(sus1) <- names(SUSpresence)
names(sus2) <- names(SUSpresence)
names(sus3) <- names(SUSpresence)
names(sus4) <- names(SUSpresence)

SUSpresence <- rbind(SUSpresence, sus1)
SUSpresence <- rbind(SUSpresence, sus2)
SUSpresence <- rbind(SUSpresence, sus3)
SUSpresence <- rbind(SUSpresence, sus4)

#Clean up file + change participant input errors
SUSpresence[c(3:8)] <- sapply(SUSpresence[c(3:8)], intRight)
SUSpresence[c(2)] <- sapply(SUSpresence$Condition, code2trial)
SUSpresence[1,2] <- "Acc"

#check normal distribution
SUSpresence$count <- as.integer(SUSpresence[3] > 5) + as.integer(SUSpresence[4] > 5) + as.integer(SUSpresence[5] > 5) + as.integer(SUSpresence[6] > 5) + as.integer(SUSpresence[7] > 5) + as.integer(SUSpresence[8] > 5)
SUSpresence$average <- rowMeans(SUSpresence[3:8])

checkNormalDistribution(SUSpresence,"count")
checkNormalDistribution(SUSpresence,"average")

SUSgroup = SUSpresence %>% group_by(Condition)

#stats 
#table(SUSpresence$ID, SUSpresence$Condition) 
friedman.test(count ~ Condition | ID, data = SUSpresence) 
res.aov <- aov(count ~ Condition, data = SUSpresence)
summary(res.aov)
summarise(SUSgroup, m=mean(count), sd=sd(count), mAvg=mean(average), sdAvg=sd(average))

pw_count <- pairwise.wilcox.test(SUSpresence$count, SUSpresence$Condition,
                           p.adjust.method = "bonferroni",
                           paired = TRUE)
pw_count
createBoxplot(SUSpresence,'count',"Presence Score",pw_count)

```

```{r}
#Load raw file from limesurvey
raw = read.csv("results_survey.csv")
offset = 69-33

##---------- Simulator Sickness ----------##
SSQ = data.frame(ID=NA, Condition=NA, SSQq1=NA, SSQq2=NA, SSQq3=NA, SSQq4=NA, SSQq5=NA, SSQq6=NA, SSQq7=NA, SSQq8=NA, SSQq9=NA, SSQq10=NA, SSQq11=NA, SSQq12=NA, SSQq13=NA, SSQq14=NA, SSQq15=NA, SSQq16=NA)
SSQ <- SSQ[FALSE,]

ssq0 <- raw[c(1,2,17:32)]
ssq1 <- raw[c(1,33,53:68)]
ssq2 <- raw[c(1,33+offset,53:68+offset)]
ssq3 <- raw[c(1,33+offset*2,53:68+offset*2)]
ssq4 <- raw[c(1,33+offset*3,53:68+offset*3)]

ssq0[2] <- rep("5", nrow(demographics)) #set 'Condition' to "Pre"

names(ssq0) <- names(SSQ)
names(ssq1) <- names(SSQ)
names(ssq2) <- names(SSQ)
names(ssq3) <- names(SSQ)
names(ssq4) <- names(SSQ)

ssq0[1] <- dm_ID
ssq1[1] <- dm_ID
ssq2[1] <- dm_ID
ssq3[1] <- dm_ID
ssq4[1] <- dm_ID

SSQ <- rbind(SSQ, ssq0)
SSQ <- rbind(SSQ, ssq1)
SSQ <- rbind(SSQ, ssq2)
SSQ <- rbind(SSQ, ssq3)
SSQ <- rbind(SSQ, ssq4)

#Clean up file + change participant input errors
SSQ[c(2:18)] <- sapply(SSQ[c(2:18)], intRight)
SSQ[c(2)] <- sapply(SSQ$Condition, code2trial)
SSQ[1+nrow(demographics),2] <- "Acc"

#Setup scoring system calculations for SSQ
nausea <- rowSums(SSQ[c(3,8:11,17,18)])
oculolomotor <- rowSums(SSQ[c(3:7,11,13)])
disorientation <- rowSums(SSQ[c(7,10,12:16)])

SSQsymptoms = data.frame(ID=SSQ[1], Condition=SSQ[2], Nausea=nausea*9.54, Oculomotor=oculolomotor*7.58, Disorientation=disorientation*13.92)#, TotalScore=NA)
SSQsymptoms$TotalScore <- rowSums(data.frame(nausea,oculolomotor,disorientation))*3.74
SSQgroup = SSQsymptoms %>% group_by(Condition)

#Stats
checkNormalDistribution5(SSQsymptoms,"TotalScore")
checkNormalDistribution5(SSQsymptoms,"Nausea")
checkNormalDistribution5(SSQsymptoms,"Oculomotor")
checkNormalDistribution5(SSQsymptoms,"Disorientation")
checkNormalDistribution(SSQsymptoms,"TotalScore")
checkNormalDistribution(SSQsymptoms,"Nausea")
checkNormalDistribution(SSQsymptoms,"Oculomotor")
checkNormalDistribution(SSQsymptoms,"Disorientation")
#table(SSQsymptoms$ID, SSQsymptoms$Condition) #sanity check

#stats 
friedman.test(TotalScore ~ Condition | ID, data = SSQsymptoms)
friedman.test(Nausea ~ Condition | ID, data = SSQsymptoms)
friedman.test(Oculomotor ~ Condition | ID, data = SSQsymptoms)
friedman.test(Disorientation ~ Condition | ID, data = SSQsymptoms)

#analyse 'Disorientation'
res.aov <- aov(Disorientation ~ Condition, data = SSQsymptoms)
summary(res.aov)
summarise(SSQgroup, m=mean(Disorientation), sd=sd(Disorientation), mAvg=mean(Disorientation), sdAvg=sd(Disorientation))

pw_disorientation <- pairwise.wilcox.test(SSQsymptoms$Disorientation, SSQsymptoms$Condition,
                           p.adjust.method = "bonferroni",
                           paired = TRUE)
pw_disorientation
createBoxplot5(SSQsymptoms,'Disorientation',"Presence Score",pw_disorientation)

```

```{r}
#-------Ranking--------#
raw = read.csv("results_survey.csv")
offset = 69-33

rankingRaw <- raw[c(1,177:180)]
ranking <- data.frame(ID=NA, Condition=NA,Rank=NA)
ranking <- ranking[FALSE,]

first <- data.frame(rankingRaw[c(1,2)],Rank="First")
second <- data.frame(rankingRaw[c(1,3)],Rank="Second")
third <- data.frame(rankingRaw[c(1,4)],Rank="Third")
fourth <- data.frame(rankingRaw[c(1,5)],Rank="Fourth")

names(first) <- names(ranking)
names(second) <- names(ranking)
names(third) <- names(ranking)
names(fourth) <- names(ranking)

first$Rank <- factor(first$Rank, c("First","Second","Third","Fourth"))
ranking <- first
ranking <- rbind(ranking, second)
ranking <- rbind(ranking, third)
ranking <- rbind(ranking, fourth)

first[c(2)] <-sapply(first$Condition, code2trial)
ranking[c(2)] <- sapply(ranking$Condition, code2trial)

ranking$numeric <- NA
ranking[ranking$Rank == "First",]$numeric <- 1
ranking[ranking$Rank == "Second",]$numeric <- 2
ranking[ranking$Rank == "Third",]$numeric <- 3
ranking[ranking$Rank == "Fourth",]$numeric <- 4


#ranking <- ranking[order(ranking$ID),]
friedman.test(numeric ~ Condition | ID, data=ranking)
pw_rank <- pairwise.wilcox.test(ranking$numeric, ranking$Condition,
                           p.adjust.method = "bonferroni",
                           paired = TRUE)
pw_rank
createBoxplot(ranking,'numeric',"Preference Ranking",pw_rank)

#ggplot(ranking, aes(fill=Condition, x=Rank)) + 
#  geom_bar(position="stack", stat="count") +
#  ggtitle("Ranking of conditions") +
#  plotTheme

rankingT <- data.frame('Accordion'=ranking[ranking$Condition=="Acc",]$Rank, check.names = FALSE)
rankingT[['Horizontal']] <- ranking[ranking$Condition=="Hor",]$Rank
rankingT[['Vertical']] <- ranking[ranking$Condition=="Ver",]$Rank
rankingT[['Stop&Reset']] <- ranking[ranking$Condition=="S&R",]$Rank


plot(likert(rankingT), col=c("#01857190", "#80cdc190", "#dfc27d90", "#a6611a90")) + ggtitle("Preference Ranking") + plotTheme



```

```{r}

```
